---
title: "Developing Data Product Final Project"
author: "Donovan Dikitanan"
date: "6/12/2020"
output: ioslides_presentation
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction

The following presentation is a guide for using my shiny application (https://jdiki001.shinyapps.io/ddp3/). 

The purpose of this application is to predict the **gas mileage** of cars in the mtcars dataset **on the basis of engine displacement**. 


## Instructions

1. Initiate the shiny application
2. Choose the value for engine displacement (0-500)
3. Check/Uncheck the boxes for the model you would like to use
4. View the plot and underlying text to find the estimated gas mileage

## Summary of Dataset (mtcars)

```{r cars, echo = TRUE}
summary(mtcars)
```


## Conclusion

As we can tell from our shiny application, a lower engine displacement volume generally correlates to higher miles per gallon. This information can be useful to those who are considering buying a new car in the future.
